\bf Are you normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-06-25 paper.qmd
added part on the need to cluster

@@

Two projections of simulated example data corresponding to the sample code: (a) Random projection where sample is inside the 2-D ellipse, (b) Optimal projection from index, showing most of the sample outside. A red cross indicates that the point is outside the p-D ellipse. The optimal projection uses mostly variables $x_4, x_5$, which is expected because these are the two directions where the sample most differs from the norm.
:::

@@

>>>>

### Additional considerations

If the observations in $W$ are primarily departing from the normal range in the same direction, the index will be expected to perform well in finding this average direction. However, if the observations have very different departures from the norm, it may be useful to break them into groups, and separately optimize on these subsets. One could consider clustering these observations using angular distance to find groups of observations that have similar directions of departure.

@@

Two projections of simulated example data corresponding to the sample code: (a) random projection where sample is inside the 2-D ellipse, (b) optimal projection from index, showing most of the sample outside. A red cross indicates that the point is outside the p-D ellipse. The optimal projection uses mostly variables $x_4, x_5$, which is expected because these are the two directions where the sample most differs from the norm.
:::

@@

### Medical patients

### Robust statistics

### Physics?

### 2024-06-25 paper.tex
added part on the need to cluster

@@

\caption{\label{fig-anomaly}Two projections of simulated example data
corresponding to the sample code: (a) Random projection where sample is
inside the 2-D ellipse, (b) Optimal projection from index, showing most
of the sample outside. A red cross indicates that the point is outside
the p-D ellipse. The optimal projection uses mostly variables
\(x_4, x_5\), which is expected because these are the two directions
where the sample most differs from the norm.}

@@

>>>>

\subsection{Additional considerations}\label{additional-considerations}

If the observations in \(W\) are primarily departing from the normal
range in the same direction, the index will be expected to perform well
in finding this average direction. However, if the observations have
very different departures from the norm, it may be useful to break them
into groups, and separately optimize on these subsets. One could
consider clustering these observations using angular distance to find
groups of observations that have similar directions of departure.

@@

\caption{\label{fig-anomaly}Two projections of simulated example data
corresponding to the sample code: (a) random projection where sample is
inside the 2-D ellipse, (b) optimal projection from index, showing most
of the sample outside. A red cross indicates that the point is outside
the p-D ellipse. The optimal projection uses mostly variables
\(x_4, x_5\), which is expected because these are the two directions
where the sample most differs from the norm.}

@@

\subsection{Medical patients}\label{medical-patients}

\subsection{Robust statistics}\label{robust-statistics}

\subsection{Physics?}\label{physics}
